\plaintitle

### 2017-04-27 statistical-quorum.tex
some figures

\subsection{Bayesian Theory}
After collecting an initial set of votes from members, we want to use that data to construct a prior distribution to help estimate the posterior probability that the proposal is acceptable to the entire community.  Because the sum of  the collected votes follows a binomial distribution, a commonplace and convenient choice for the form of the prior on the community's bias is the Beta distribution (due to its conjugacy with the binomial distribution).

@@

For our purposes, we make a natural choice,
\begin{align}\label{eq6}
\lambda (t) = \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}},
\end{align}
where
\begin{description}
\begin{itemize}
\item[$\lambda_0 =$] a time-averaged rate of vote arrivals (preferably over a unit of time that sufficiently smooths the historical rate),
\item[$\gamma =$] a decay factor ($0 < \gamma < 1$) ideally tuned to fit real historical data for the community via a regression analysis.
\end{itemize}
\end{description}
Now, for example, to upper bound with $95\%$ probability the remaining number of votes still pending, we solve for $\hat{K_i}$ to satisfy the following inequality:
\begin{align}\label{eq7}
\lim_{t\rightarrow \infty}\Pr\left(N(t)\leq \hat{K_i}\right) & = \sum_{n=0}^{\hat{K_i}} \frac{(\lambda_0 \cdot K_i/N_i)^n}{n!(\ln{1/\gamma})^n}e^{-\lambda_0 \frac{K_i/N_i}{\ln{1/\gamma}}}\\
& \geq 95\% \nonumber
\end{align}
Upon solving for $\hat{K_i}$, we set $N_i = \alpha_i + \beta_i + \hat{K_i}$, and can proceed to check for a statistical quorum.

>>>>

\subsection{Bayesian Theory}
After collecting an initial set of votes from members, we want to use that data to construct a prior distribution to help estimate the posterior probability that the proposal is acceptable to the entire community.  Because the sum of  the collected votes follows a binomial distribution, a commonplace and convenient choice for the form of the prior on the community's bias is the Beta distribution (due to its conjugacy with the binomial distribution).  Together, they form the Beta-binomial distribution (related to the P\'olya urn model).

@@

For our purposes, we make a natural choice,
\begin{align}\label{eq6}
\lambda (t) = \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}},
\end{align}
where
\begin{description}
\begin{itemize}
\item[$\lambda_0 =$] a time-averaged rate of vote arrivals (preferably over a unit of time that sufficiently smooths the historical rate),
\item[$\gamma =$] a decay factor ($0 < \gamma < 1$) ideally tuned to fit real historical data for the community via a regression analysis.
\end{itemize}
\end{description}
Now, for example, to upper bound with $95\%$ probability the remaining number of votes still pending, we solve for $\hat{K_i}$ to satisfy the following inequality:
\begin{align}\label{eq7}
\lim_{t\rightarrow \infty}\Pr\left(N(t)\leq \hat{K_i}\right) & = \sum_{n=0}^{\hat{K_i}} \frac{\Lambda^n}{n!}e^{-\Lambda}\\
& \geq 95\% \nonumber
\end{align}
where $\Lambda = \frac{\lambda_0 \cdot K_i/N_i)}{\ln{1/\gamma}}$.
Upon solving for $\hat{K_i}$, we update $N_i \leftarrow \min\{N_i,\alpha_i + \beta_i + \hat{K_i}\}$, and can proceed to check for a statistical quorum.
